DOpElib:\\ Differential Equations and Optimization Environment

### 2016-04-08 Examples/Documentation/introduction.tex
Minor Typo in description

A configuration of deal.II working with \texttt{DOpElib} can be obtained with
the following commands assuming that one is currently in the 
directory where the deal.II sources are located.
\begin{lstlisting}
mkdir build
mkdir install
cd build
cmake -DCMAKE_INSTALL_PREFIX=../install -DDEAL_II_WITH_UMFPACK=true -DDEAL_II_FORCE_BUNDLED_UMFPACK=true  ../
make install
\end{lstlisting}
If in addition, features are desired corresponding flags need to be passed to cmake. If, for 
example Trilinos solvers are desired, the above cmake command needs to have the additional flags

>>>>

A configuration of deal.II working with \texttt{DOpElib} can be obtained with
the following commands assuming that one is currently in the 
directory where the deal.II sources are located.
\begin{lstlisting}
mkdir build
mkdir install
cd build
cmake -DCMAKE_INSTALL_PREFIX=../install \ 
      -DDEAL_II_WITH_UMFPACK=true \
      -DDEAL_II_FORCE_BUNDLED_UMFPACK=true  ../
make install
\end{lstlisting}
If in addition, features are desired corresponding flags need to be passed to cmake. If, for 
example Trilinos solvers are desired, the above cmake command needs to have the additional flags
